Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
pass

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google), \smonkey{}
(Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the
breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per
technique (\ref{fig:stacked-technique}).  Each stacked bar breaks down
the bugs per status (\eg{}, ``1-New''). The prefix number indicates
the ordering that status labels are assigned. Several of these reports
have the label ``3-Fixed'', indicating that bug fixes have been
incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{}\footnote{Microsoft announced in
  December 2018 that the Edge browser will be based on Chromium and
  ChakraCore development would be
  discontinued~\cite{chakra-discontinued}.} and JavaScriptCore (\jsc).
We reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed), \noBugsBugsReportedHermes in
\hermes (\noBugsBugsConfirmedHermes confirmed), and
\noBugsBugsReportedSMonkey in \smonkey{} (\noBugsBugsConfirmedSMonkey confirmed).
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation bugs (of which,
\noBugsTransplantationConfirmed were confirmed and
\noBugsTransplantationFixed were fixed) whereas differential testing
revealed \noBugsDifferentialTesting bugs (of which,
\noBugsDifferentialTestingConfirmed were confirmed and
\noBugsDifferentialTestingFixed were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of fixed bugs were similar, if we consider only those confirmed
or fixed. Most bugs we found are of moderate severity.

@@

\emph{Key Findings.}~We found that--1)~Differential testing and Test
Transplantation are practical and effective techniques to find bugs on real,
complex, and widely used software systems and 2)~Even for problems with
fairly clear specifications, as in \javascript{}, there is likely (a
lot of) variation between different implementations, which brings intrinsic
challenges to developers that work on them.
Section~\ref{sec:lessons} expands and elaborates key
findings and lessons learned.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of test transplantation and differential testing in
revealing functional bugs in popular \javascript\ engines.  Additional
contributions include: 1)~A number of bugs found and fixed.  We
reported a total of \totalBugsReported bugs.  Of these,
\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
fixed.  2)~An infrastructure for performing test transplantation and
differential testing. The soruce code produced and the generated data sets of tests
and bugs are publicly available online at the following link:

>>>>

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google), \smonkey{}
(Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the
breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per
technique (\ref{fig:stacked-technique}).  Each stacked bar breaks down
the bugs per status (\eg{}, ``1-New''). The prefix number indicates
the ordering that status labels are assigned. Several of these reports
have the label ``3-Fixed'', indicating that bug fixes have been
incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{}\footnote{Microsoft announced in
  December 2018 that the Edge browser will be based on Chromium and
  ChakraCore development would be
  discontinued~\cite{chakra-discontinued}.} and JavaScriptCore (\jsc).
We also reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed), \noBugsBugsReportedHermes
bugs in \hermes (\noBugsBugsConfirmedHermes confirmed), and
\noBugsBugsReportedSMonkey bugs in \smonkey{}
(\noBugsBugsConfirmedSMonkey confirmed).  Our results show that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation bugs
(of which, \noBugsTransplantationConfirmed were confirmed and
\noBugsTransplantationFixed were fixed) whereas differential testing
revealed \noBugsDifferentialTesting bugs (of which,
\noBugsDifferentialTestingConfirmed were confirmed and
\noBugsDifferentialTestingFixed were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of confirmed or fixed bugs are similar. Most bugs we found are
of moderate severity.

@@

\emph{Key Findings.}~To sum up, we found that 1)~Differential testing
and Test Transplantation are practical and effective techniques to
find bugs on real, complex, and widely used software systems and
2)~Even for problems with fairly clear specifications, as in
\javascript{}, there is likely (a lot of) variation between different
implementations, which brings intrinsic challenges to developers that
work on them.  Section~\ref{sec:lessons} expands and elaborates our
key findings and lessons learned.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is
empirical: we provide a comprehensive study analyzing the
effectiveness of test transplantation and differential testing in
revealing functional bugs in popular \javascript\ engines.  Additional
contributions include: 1)~A number of bugs found and fixed.  We
reported a total of \totalBugsReported bugs.  Of these,
\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
fixed.  2)~An infrastructure for performing test transplantation and
differential testing. The source code produced and the generated data sets of tests
and bugs are publicly available online at the following link:
